### 2020-09-03 thesis/thesis.tex
[thesis] Final submitted version

    Linear usages of resumptions is asserted by analyzing parsed AST tree,
    where in every leaf there must be a return statement. It's value is then
    passed into continuation of a cohandler.

>>>>

    The idea is that linear usages of resumptions can be easily asserted by
    analyzing parsed AST tree, where in every leaf there must be a return
    statement. It's value then can be passed into continuation of a cohandler.
    That being said, it is not implemented as of the day of submitting the
    thesis.
